---
title: "Costs in parents"
author: "Ivan Bizberg"
date: "10/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Library
```{r include=FALSE}
library(tidyverse)
library(magrittr)
library(lubridate)
library(dtplyr)
library(data.table)

library(usethis)
# Data analysis
library(performance)
library(bbmle)
library(sjPlot)

library(glmmTMB)
library(lme4)
library(effects)
library(ordinal)
```
```{r}
path <- "ivan"
```


# Import data 
```{r}
# Data set for analysis (For sabbatical year model we need another data set)
NewMother = read_csv(str_glue("C:/Users/{path}/Dropbox/PHD/DATA/Csv/DATAFemaleCosts.csv"))
NewMother %>% names()
Rawdata = NewMother %>%
  distinct(ANILLOHEMB, WORKYEAR, .keep_all = T) %>% # because I want to use year variables 
  filter(!ANILLOHEMB %in% c("SA")) %>% 
  filter(!str_detect(ANILLOHEMB, "X")) %>% 
  # filter(CONFIRMMACH == T) %>%
  filter(!(SEMANIPULO == T & LastSEMANIPULO == T)) %>%
  filter(!Nest_OrderFemale > 1) %>%
  mutate_at(vars(ReprodLastYear, LastBroodReductionYear, WORKYEAR, ANILLOHEMB, LastClutchYear, LastBroodYear), as.factor) %>%
  # Test another paper
    filter(LastClutchYear == 2 & LastBroodYear == 2 #& LastBroodReductionYear == "Partial"
    # filter(PUESTA == 2 & NIDADA == 2 #& BroodReduction == "Partial"
           ) %>%
  select(
    # Dependent variables
    # ChangePartener,
    PROPORTIONALRANK,
    NIDADA,
    PUESTA,
    Recruits,
    LastRecruits,
    FLEDGED,
    ChicksBodyCondition,
    SabNextYear,
    BroodReduction,
    ReprodLastYear,
    BroodReductionBin,
    # Reduction,
    ### Independent variables
    LastClutchYear,LastBroodYear,
    LastBroodReductionYear,
    # LastParentalCare_ALL,
    # LastParentalCare_Egg,
    LastParentalCare_Chick, BroodReduction,
    ParentalCare_Chick,
    LastProportionalRankYear,
    RealMotherAge, 
    # RealFatherAge,
    CoupleExpLocal,
    ### Random variables
    WORKYEAR,
    ANILLOHEMB) 


# Remove errors
data <- Rawdata %>% filter(!LastParentalCare_Chick < 0)
```

# Data exploration 
```{r}

# Effect of last brood in present clutch size 
data %>% select(LastBroodYear, LastBroodReductionYear, PUESTA, RealMotherAge) %>% filter(!is.na(RealMotherAge)) %>%
  ggplot(aes(LastBroodYear, PUESTA, color = factor(LastBroodReductionYear))) + geom_jitter(alpha = 0.6) +
  geom_smooth(method = "lm")

# Relationship between mother's age and number of fledged
data %>% ggplot(aes(factor(RealMotherAge), fill = factor(FLEDGED))) + 
  geom_histogram(stat = "count", position = "fill")

# How chick survival varie through mothers age
data %>% rowwise() %>% mutate(LASTAGE = mean(c(LastAge1, LastAge2, LastAge3), na.rm = T)) %>% 
  group_by(RealMotherAge) %>% summarise(mean(LASTAGE, na.rm = T)) %>% 
  ggplot(aes(RealMotherAge, `mean(LASTAGE, na.rm = T)`)) + geom_col()

# Check for outliers 
NewMother %>% ggplot(aes())
```

# I Analysis Change Partner
```{r}
ProsData = data %>% 
  select(-NIDADA, -PUESTA, -Recruits, -LastRecruits, -FLEDGED, -ChicksBodyCondition, -SabNextYear, -BroodReduction) %>%
  mutate(across(c(where(is.numeric), -ChangePartener), arm::rescale)) %>% drop_na

mod_ChPa1 = glmmTMB(ChangePartener ~ LastBroodYear + LastBroodReductionYear + LastBroodYear : LastBroodReductionYear +
                      LastProportionalRankYear + LastPartnerAge + RealMotherAge + (1|ANILLOHEMB) + (1|WORKYEAR),
                 family = binomial, REML = F,
                 data = Prepro)

mod_ChPa2 = update(mod_ChPa1, . ~ . - LastBroodYear : LastBroodReductionYear)
mod_ChPa3 = update(mod_ChPa2, . ~ . - (1|WORKYEAR))
mod_ChPa4 = update(mod_ChPa2, . ~ . - (1|ANILLOHEMB))
mod_ChPa5 = update(mod_ChPa2, . ~ . - (1|ANILLOHEMB) - (1|WORKYEAR))


check_collinearity(mod_ChPa2)
AICctab(mod_ChPa1, mod_ChPa2,mod_ChPa3, mod_ChPa4, mod_ChPa5)
anova(mod_ChPa1, mod_ChPa2)


summary(mod_ChPa2)
# plot(allEffects(mod_ChPa), type = "response")

```
We can see that the most important variables are brood size / parental care / TOTAL brood reduction. More nestlings and more parental care reduce the risk of partner change, Total brood reducion increase the chances of partner change

# II Analysis PROPORTIONALRANK----
```{r}
ProsData = data %>% 
  select(-NIDADA, -PUESTA, -Recruits, -LastRecruits, -FLEDGED, -ChicksBodyCondition, -SabNextYear, -BroodReduction) %>%
  mutate(across(c(where(is.numeric), -PROPORTIONALRANK), arm::rescale)) %>% drop_na

Mod_PropRank = glmmTMB(PROPORTIONALRANK ~ LastBroodReductionYear + 
                         LastProportionalRankYear + 
                         LastParentalCare_Chick +
                         CoupleExpLocal +
                         RealMotherAge + 
                         I(RealMotherAge^2) + 
                       (1|ANILLOHEMB) + (1|WORKYEAR),
                      family = beta_family(), REML = F,
                     data = ProsData)
check_collinearity(Mod_PropRank)


summary(Mod_PropRank)
tab_model(Mod_PropRank)
plot(allEffects(Mod_PropRank))
```

# III  Analysis Clutch size
```{r}
ProsData %<>% mutate(fct_relevel(LastBroodReductionYear, "NO", after = 2)) 
ProsData = data %>% 
  select(-NIDADA, -Recruits, -LastRecruits, -FLEDGED, -ChicksBodyCondition, -SabNextYear, -BroodReduction) %>% 
  mutate(across(c(where(is.numeric), -PROPORTIONALRANK), arm::rescale)) %>% drop_na

Mod_Clutch = lmer((PUESTA) ~ LastBroodReductionYear + #LastBroodYear * 
                    # LastParentalCare_Chick +
                     + PROPORTIONALRANK + LastProportionalRankYear + #CoupleExpLocal +
                      RealMotherAge + I(RealMotherAge^2) +
                      (1|ANILLOHEMB) + (1|WORKYEAR),
                    # REML = F,
                    data = ProsData)
check_collinearity(Mod_Clutch)


summary(Mod_Clutch)
tab_model(Mod_Clutch)
# plot(allEffects(Mod_Clutch))
```

# IV  Analysis Brood size
```{r}
ProsData = data %>% 
  select(-PUESTA, -Recruits, -LastRecruits, -FLEDGED, -ChicksBodyCondition, -SabNextYear, -BroodReduction, -LastParentalCare_Chick) %>% 
  mutate(across(c(where(is.numeric), -NIDADA), arm::rescale)) %>% drop_na

Mod_Brood = glmmTMB((NIDADA) ~ #LastBroodYear + 
                      PROPORTIONALRANK + 
                      # LastParentalCare_Chick + 
                      # LastParentalCare_Chick : LastBroodReductionYear +
                      LastBroodReductionYear + LastProportionalRankYear + 
                      CoupleExpLocal +
                      RealMotherAge + I(RealMotherAge^2) +
                      (1|ANILLOHEMB) + (1|WORKYEAR),
                    family = poisson, REML = F,
                    data = ProsData)
check_collinearity(Mod_Brood)


summary(Mod_Brood)
tab_model(Mod_Brood)
plot(allEffects(Mod_Brood))
```
Mother age and last year parental care of chicks have an positive and negative effect respectively on brood size (similar result for parental care with poisson distribution)





# V Analysis Chicks Body Condition
```{r}
ProsData = data %>% 
  select(-PUESTA, -Recruits, -LastRecruits, -FLEDGED, -NIDADA, -SabNextYear, -BroodReduction) %>% 
  mutate(across(c(where(is.numeric), -ChicksBodyCondition), arm::rescale)) %>% drop_na

# Check distribution
ProsData %>% ggplot(aes(ChicksBodyCondition)) + geom_histogram() 
Mod_Brood = lmer(ChicksBodyCondition ~ #LastParentalCare_Chick + 
                   # LastBroodYear +
                   PROPORTIONALRANK + LastBroodReductionYear + CoupleExpLocal +
                      RealMotherAge +
                      # (1|ANILLOHEMB) + 
                   (1|WORKYEAR),
                    REML = F,
                    data = ProsData)
check_collinearity(Mod_Brood)


tab_model(Mod_Brood)
# plot(allEffects(Mod_Brood))
```
Chick body condition doesn't get affected by previous brood reduction. We are starting to see a patron body condition of the chicks is rarely getting affected. Maybe an effect of brood reduction


# VI Analysis Fledglings 
```{r}
ProsData = data %>% 
  select(-PUESTA, -Recruits, -LastRecruits, -ChicksBodyCondition, -NIDADA, -SabNextYear, -BroodReduction) %>% 
  mutate(across(c(where(is.numeric), -FLEDGED), arm::rescale)) %>% drop_na

data %>% ggplot(aes(FLEDGED)) + geom_histogram()

Mod_Fledg = glmmTMB(FLEDGED ~ PROPORTIONALRANK + 
                      # LastParentalCare_Chick +
                      LastBroodReductionYear + LastProportionalRankYear + 
                      # LastBroodReductionYear : LastParentalCare_Chick + 
                      CoupleExpLocal +
                      RealMotherAge + I(RealMotherAge^2) +
                      (1|ANILLOHEMB) + (1|WORKYEAR),
                    family = poisson, REML = F,
                    data = ProsData)

check_collinearity(Mod_Fledg)
summary(Mod_Fledg)
```
Last year brood size has a positive effect on the number of fledglings.

# VII Analysis brood reduction 
```{r}
ProsData = data %>% 
  select(-PUESTA, -Recruits, -LastRecruits, -ChicksBodyCondition, -NIDADA, -SabNextYear) %>% 
  mutate(across(c(where(is.numeric), -BroodReductionBin), arm::rescale)) %>% drop_na

Mod_Brood = glmmTMB(BroodReductionBin ~ #LastBroodYear + 
                      PROPORTIONALRANK + 
                      # LastParentalCare_Chick +
                      LastBroodReductionYear + LastProportionalRankYear + 
                      CoupleExpLocal +
                      RealMotherAge + I(RealMotherAge^2) +
                      (1|ANILLOHEMB) + (1|WORKYEAR),
                    family = binomial(link="probit"),REML = FALSE, 
                    data = ProsData)

check_collinearity(Mod_Brood)
summary(Mod_Brood)
```
# VIII Analysis Recruits at 6 years old
```{r}
ProsData = data %>% mutate_at(vars(WORKYEAR, ANILLOHEMB, ReprodLastYear), as.factor) %>%
  mutate(across(c(where(is.numeric), -Recruits), arm::rescale)) %>%  
  mutate(BiRecruits = if_else(Recruits > 0, 1, 0)) %>% 
  mutate(BiLastRecruits = if_else(LastRecruits > 0, 1, 0)) %>% 
  filter(!WORKYEAR > 2013) # need to avoid including chicks that can't yet be recruits
  
ProsData %>% ggplot(aes(BiLastRecruits)) + geom_histogram()

Mod_Brood = glmmTMB(BiRecruits ~ #LastBroodYear * LastBroodReductionYear +
                      PROPORTIONALRANK + #BiLastRecruits + 
                      LastParentalCare_Chick +
                      # LastBroodReductionYear + #LastProportionalRankYear + 
                      CoupleExpLocal +
                      RealMotherAge + I(RealMotherAge^2) +
                      (1|ANILLOHEMB) + (1|WORKYEAR),
                    family = binomial(link="probit"),REML = FALSE, 
                    data = ProsData)

check_collinearity(Mod_Brood)
summary(Mod_Brood)
```

# VIV Analysis next year reproduction (sabbatical)
```{r}
NewMother %>% names()
ProsData = data %>% 
  select(c(-contains("Last"), -PUESTA, -Recruits, -ChicksBodyCondition, -NIDADA, -FLEDGED)) %>% 
  mutate(across(c(where(is.numeric), -SabNextYear), arm::rescale)) %>% drop_na

Mod_Brood = glmmTMB(SabNextYear ~ #LastBroodYear + 
                      # PROPORTIONALRANK + 
                      ParentalCare_Chick +
                      BroodReduction + 
                      CoupleExpLocal +
                      RealMotherAge + I(RealMotherAge^2) +
                      (1|ANILLOHEMB) + (1|WORKYEAR),
                    family = binomial(link="probit"),REML = FALSE, 
                    data = ProsData)

check_collinearity(Mod_Brood)
summary(Mod_Brood)
```

# Results
Early results suggest that the trade off between parental care and future reproduction is masked by individual females quality.  

